\personalAcknowledgementEnglish{
I would like to thank the amazing people who made my doctoral research period both fruitful and enjoyable.
\begin{itemize}
    \item I would like to thank my advisor, Idit Keidar, for her amazing guidance and for teaching me to be a researcher. Thank you for being an inspiring role model, and for all your patience. It was my greatest pleasure to learn from you.
    
    \item I wish to thank Sasha, Eddy, Eschar, Lee, Hadar, Dor, Ori, Dahlia, Tomer, Guy, Gal, Roee, Paula, Lior, Dan, Jacob, Daehyeok, Shir, Alon, Igot, and Mark, for productive and enjoyable collaborations during my research.
    
    \item I would like to thank my research group's team members for the fun times during team meetings, during lunches, and during coffee breaks. Specifically, I would like to thank Gal, Ramy, and Shaked, for our professional discussions. I also thank Ramy and Shaked for being great office mates.
    
    \item I wish to thank Orly and Adi for their administrative support. Thank you for your dedication and speedy answers.
    
    \item I would like to thank my parents, Richard and Emma, for believing in me and for doing a great job raising me. Thank you for the encouraging words you had to offer whenever I needed them.
    
    \item I wish to thank my parents-in-law, Deborah and Elan, for their kind support and assistance.
    
    \item I would like to thank all my family, Aaron, Carmella, Maya, Lee, Lior, Rachel, Dean, Aria, Joseph, and Avishai, for making my breaks from the Technion enjoyable.
    
    \item I wish to thank my lovely children, Rephael \Smiley[1.5] and Nesya \Smiley[1.5], for providing me with pure joy and happiness.
    
    \item Finally, and most importantly, I wish to thank my darling wife Noa. Your support and sacrifice throughout my doctorate is what made it possible. I am constantly amazed by you, and am grateful to have you by my side.
\end{itemize}
}

\personalAcknowledgementHebrew{

אני רוצה להודות למנחה שלי, להוריי, לחבריי, וכו' וכו'.

אפשר להוסיף עוד תודות והערות אישיות כאן.

שים/י לב: קטע זה של תודות מודפס בפועל רק בגרסת החיבור שלאחר-הבחינה (הווה אומר רק אם הסרת את האפשרות \textenglish{\texttt{beforeDefense}} מן האפשרויות המועברות ל-\textenglish{\texttt{document class}} בקובץ \textenglish{\texttt{thesis.tex}}.)
}
