\section{Background: sequential sketches}
\label{fc-sec:background}

A sketch $S$ summarizes a collection of elements $\Collection{a_1,a_2,\dots,a_n}$, processed
in some order given as a stream $A=a_1,a_2,\dots,a_n$.
The desired summary is agnostic to the processing order,
but the underlying data structures may differ due to the order. Its API is:

\begin{description}
\item[$S$.init()] initializes $S$ to summarize the empty stream;
\item[$S$.update($a$)] processes stream element $a$;
\item[$S$.query($arg$)] returns the function estimated by the sketch over the stream processed thus far, e.g., the number of unique elements; 
 takes an optional argument, e.g., the requested quantile.
 \item[$S$.merge($S'$)] merges sketches $S$ and $S'$ into $S$; i.e., if $S$ initially summarized stream $A$ and $S'$ 
 summarized $A'$, then after this call, $S$ summarizes the concatenation of the two, $A||A'$.
\end{description}

\paragraph{Example: $\Theta$ sketch.}

\begin{algorithm}[htb]
    \small
    %\begin{multicols}{2}
    \begin{algorithmic}[1]
        %\begin{varwidth}[t]{0.9\linewidth} 
        \Vars
        \State   sampleSet, init $k$ $1$'s \Comment samples
        \State  $\Theta$, init $1$			\Comment threshold
        \State {\tt atomic} est, init $0$ \Comment estimate
        \State $h$, init random uniform hash function 
        \EndFor
        
        \Procedure{query}{arg}
        \State \Return $est$ \label{fc-l:query}
        \EndProcedure
        
        \Procedure{update}{arg}
        \If{$h$(arg) $\geq \Theta$} \Return
        \EndIf
        \State add $h$(arg) to \emph{sampleSet}
        \State keep $k$ smallest samples in \emph{sampleSet}
        \State $\Theta \leftarrow max(sampleSet)$
        \State $\mathit{est}$ $\leftarrow $ $\left( |\text{sampleSet}|-1 \right)$ / $\Theta$
        \EndProcedure
        %\end{varwidth}\quad\quad\quad 
        %\columnbreak
        %\begin{varwidth}[t]{1\linewidth}

        \Procedure{merge}{S}
        \State sampleSet $\leftarrow$ merge sampleSet and $S$.sampleSet
        \State keep $k$ smallest values in sampleSet
        \State $\Theta \leftarrow max($sampleSet$)$
        \State $\mathit{est}$ $\leftarrow $ $\left( |\text{sampleSet}|-1 \right)$ / $\Theta$ \label{fc-l:update-est}
        \EndProcedure
        
    \end{algorithmic}
    %\end{multicols}
    \caption{$\Theta$ sketch.}
    \label{fc-alg:theta}
\end{algorithm}

Our running example is a $\Theta$ sketch based on the 
\emph{K Minimum Values (KMV)} algorithm~\cite{KMV} given in Algorithm~\ref{fc-alg:theta}. It maintains a \emph{sampleSet} and a parameter $\Theta$
that determines which elements are added to the sample set. 
It uses a random hash function $h$ whose outputs are uniformly distributed
in the range $[0,1]$, and $\Theta$ is always in the same range.  
An incoming stream element is first hashed, and then the hash is compared to $\Theta$. 
In case it is smaller, the value is added to \emph{sampleSet}.  Otherwise, it is ignored. 

Because the hash outputs are uniformly distributed, the expected proportion of values
smaller than $\Theta$ is $\Theta$. 
Therefore, we can estimate the number of unique elements in the stream by
dividing the number of (unique) stored samples by $\Theta$ (assuming that the random hash function is
drawn independently of the stream values).

KMV $\Theta$ sketches keep constant-size sample sets:
they take a parameter $k$ and keep the $k$ smallest hashes seen so far. 
$\Theta$ is $1$ during the first $k$ updates, and 
subsequently it is the hash of the largest sample in the set.
Once the sample set is full,
every update that inserts  a new element also removes the largest
one and updates $\Theta$. This is implemented efficiently using a min-heap.
The merge method adds a batch of samples to \emph{sampleSet}.

\paragraph{Accuracy.}

% Sequential specification
Today, sketches are used sequentially,
so that the entire stream is processed 
and then $S$.query(arg) returns an estimate of the desired function 
on the entire stream. Accuracy is defined in one of two ways.
One approach analyses the \emph{Relative Standard Error (RSE)} of the estimate, 
which is the standard error normalized by the quantity being estimated.
For example, a KMV $\Theta$ sketch with $k$ samples has an RSE of less than $1/\sqrt{k-2}$~\cite{KMV}.

 A PAC sketch provides a result that estimates the correct result
within some error bound $\epsilon$ with a failure probability bounded by some parameter $\delta$.  
For example, a Quantiles sketch approximates the $\phi$th quantile of a stream with $n$ elements 
by returning an element whose rank is in $\left[(\phi-\epsilon)n , (\phi+\epsilon)n \right]$ with 
probability at least $1-\delta$~\cite{agarwal2013mergeable}.